Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-29 latex/comp_or.tex
Comp OR paper update

In this work, we explore computer parallelism in solving the problem involving scheduling the loading and routing of an airplane in a tour of simultaneous pickup and delivery at intermediate hubs while taking into account a utility score, weight and balance rules, and fuel usage.

@@

In this work, we raise four hypotheses for improvements to the work of \cite{MesquitaSanches2023}: 
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) A procedure for 3D packing running in parallel mode would keep the run time adequate for operational use.
(4) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.

@@

These improvements in their heuristics are meant to reduce the stress that transport planners are subjected to, because they have to deal with a lot of information in planning the aircraft route, assembling the pallets, and picking up and delivering at each node. To the best of our knowledge, that is the first time that an air cargo transport problem that simultaneously involves APP, WBP, PDP, TSP, and 3D packing has been addressed, and the first time ACLP+RPDP is solved with computer parallelism.

@@

Below, we present the implementation for $SolveNode$, the new parallel heuristic that we propose called {\it Multiprocessing Shims (mpShims)}.

@@

We solved all scenarios and instances with a MIP solver in a relaxed linear model. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

@@

Another important fact is the inversion of quality results between {\it Shims} and {\it mpShims}. In Table \ref{tab:results}, {\it Shims} was better, but, in Table \ref{tab:results2} (with the inclusion of the {\it Multiprocessing 3D packing}), {\it mpShims} surpassed {\it Shims}' results. The rationale behind this is that .....

@@

Other important contributions are that we verified four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; a procedure for 3D packing was turned possible for operational use due to a process-based parallel computing heuristic, and the integer programming procedure to minimize pallets' travel in the cargo bay was successful.

>>>>

In this work, we explore process-based parallel computing in solving the problem involving scheduling the loading and routing of an airplane in a tour of simultaneous pickup and delivery at intermediate hubs while taking into account a utility score, weight and balance rules, and fuel usage.

@@

In this work, we raise four hypotheses for improvements to the work of \cite{MesquitaSanches2023}: 
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) A procedure for 3D packing running in process-based parallel computing mode would keep the run time adequate for operational use.
(4) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.

@@

These improvements in their heuristics are meant to reduce the stress that transport planners are subjected to, because they have to deal with a lot of information in planning the aircraft route, assembling the pallets, and picking up and delivering at each node. To the best of our knowledge, that is the first time that an air cargo transport problem that simultaneously involves APP, WBP, PDP, TSP, and 3D packing has been addressed, and the first time ACLP+RPDP is solved with process-based parallelism.

@@

Below, we present the implementation for $SolveNode$, the new process-based parallel heuristic that we propose called {\it Multiprocessing Shims (mpShims)}.

@@

We solved all scenarios and instances with a MIP solver in a relaxed linear model. This is good for the reader to have an idea of the real performance differences between serial and process-based parallel {\it Shims}.

@@

Another important fact is the inversion of quality results between {\it Shims} and {\it mpShims}. In Table \ref{tab:results}, {\it Shims} was better, but, in Table \ref{tab:results2} (with the inclusion of the {\it Multiprocessing 3D packing}), {\it mpShims} surpassed {\it Shims}' results.

The rationale behind this is that, in sequential mode ({\it Shims}), items with smaller volumes (higher edge attractiveness $\eta_{ij}^{\pi_k}$, Equation \ref{eq:edge}) tend to be assigned first to central pallets, and items with bigger volumes tend to be assigned to the ramp door or to the forward-positioned pallets; these bigger items are more difficult for the 3D packer actions. On {\it mpShims}, as all pallets are built in parallel, the size distribution is more uniform, with a better size diversity to be allocated to each pallet, which is less difficult for the 3D packer actions due to the variety of item dimensions for packing. This explains why {\it mpShims} exceeded {\it Shims}' results after the {\it Multiprocessing 3D packing}.

@@

Other important contributions are that we verified four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; a 3D packing method was turned possible for operational use due to a process-based parallel computing heuristic, and the integer programming procedure to minimize pallets' travel in the cargo bay was successful.
